\let\cleardoublepage\clearpage
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

% Helpers
I would like to express my deepest gratitude to Angela Altamirano for creating the wonderful cover art. Special thanks to Stephanie Pierucci and Russell Womack for their tireless efforts in publishing, and to Dan Bernard and Michael Townsend for their invaluable support with the audiobook.

% Supporters
My sincere appreciation goes to my early supporters: William Dickson, Daniel Hoevel, Patrick Maloney, Jerrod Howlett, and Jeff Zinser. A special thank you to Louis Cid and the Harvard Club of New York for providing me with an early forum. I am also grateful to the Data Meetup Philadelphia and Joe Eubel for their encouragement. Dr. Elisa Esposito deserves a heartfelt thank you for her constant support.

% Teachers
I would like to express my profound gratitude to Dr. Péter Érdi for taking me under his wing many years ago. I am also especially indebted to the following educators: Ron Conwell, Tim Leunig, Alyce Brady, Pam Cutter, and Cade Massey.

% Colleagues and Students
I would like to acknowledge my bootcamp students, your effort is inspiring and you all are certainly in the right field at the right time. Also my current and former colleagues: Liubomyr Pohreliuk, Davide Anastasia, Matthew Griffiths, Jonathan Bloch, and Anthony Lauzon for their invaluable insights and contributions.

% Software
Lastly, I would like to extend my gratitude to the open source software community and the Free Software Foundation. This book uses the kaobook LaTeX project and many Free and Open Source AI models for text and image generation like Stable Diffusion and Mann-E. Special thanks to the Linux Foundation, PyTorch Foundation, Google for Tensorflow, Meta and Yann LeCun for LLaMA, and OpenAI.
