\setchapterpreamble[u]{\margintoc}
\chapter{The data is the hardest part}
\labch{intro}

You are essentially programming with data, so if your data sucks so will your prediction, you also really can't generalize, only correllate.

are you predicting the right thing? Are you really predicting how valuable the company is or just whether it'll be the next meme stock?

“I hope for some sort of peace—but I fear that machines are ahead of morals by some centuries and when morals catch up there'll be no reason for any of it.” Harry Truman, 1945 \sidecite{McCullough1992}

Representation, "fixing the training set" \sidecite{Christian2020}, or the Impossibility of Fairness from a model.

TODO talk about these books
\cite{Oneil2017}
\cite{Perez2019}
\cite{Blackman2022Jul}
\cite{Christian2020}



"The second requirement of goal-misalignment risk is that an intelligent machine can commandeer the Earth's resources to pursue its goals, or in other ways prevent us from stopping it... We have similar concerns with humans. This is why no singer person or entity can control the entire internet and why we require multiple people to launch a nuclear missile. Intelligent machines will not develop misaligned goals unless we go to great lengths to endow them with that ability. Even if they did, no machine can commandeer the world's resources unless we let it. We don't let a single human, or even a small number of humans, control the world's resources. We need to be similarly careful with machines." \cite{hawkins_2022}

\begin{lstlisting}[style=kaolstplain,linewidth=1.5\textwidth]
cd myproject
docker run tensorflow
#profit!
\end{lstlisting}

\url{tex.stackexchange.org} for help.

