\setchapterpreamble[u]{\margintoc}
\chapter{Machine Learning Methods}
\labch{intro}


are you predicting the right thing? Are you really predicting how valuable the company is or just whether it'll be the next meme stock?

“I hope for some sort of peace—but I fear that machines are ahead of morals by some centuries and when morals catch up there'll be no reason for any of it.” Harry Truman, 1945 \sidecite{McCullough1992}

Representation, "fixing the training set" \sidecite{Christian2020}, or the Impossibility of Fairness from a model.

TODO talk about these books
\cite{Oneil2017}
\cite{Perez2019}
\cite{Blackman2022Jul}
\cite{Christian2020}



"AI Scientists disagree as to whether these language networks posess true knowledge or are just mimicking humans by remembering the statistics of millions of words. I don't beloive any kind of deep learning network will achieve the goal of AGI if the network doesn't model the world the way the brain does. Deep learning networks work well, but not because they solved the knowledge representation problem. They work well because they avoided it completely, relying on statistics and lots of data instead. How deep learning networks work is clever, their performance impressive, and they are commercially valuable. I am only pointing out that they don't possess knowledge and, therefore, are not on the path to having the ability of a five-year-old child." \cite{hawkins_2022}


"The second requirement of goal-misalignment risk is that an intelligent machine can commandeer the Earth's resources to pursue its goals, or in other ways prevent us from stopping it... We have similar concerns with humans. This is why no singer person or entity can control the entire internet and why we require multiple people to launch a nuclear missile. Intelligent machines will not develop misaligned goals unless we go to great lengths to endow them with that ability. Even if they did, no machine can commandeer the world's resources unless we let it. We don't let a single human, or even a small number of humans, control the world's resources. We need to be similarly careful with machines." \cite{hawkins_2022}

\begin{lstlisting}[style=kaolstplain,linewidth=1.5\textwidth]
cd myproject
docker run tensorflow
#profit!
\end{lstlisting}

\url{tex.stackexchange.org} for help.

