\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface} % Add the preface to the table of contents as a chapter

This book is an attempt to organize my brain on paper. I have been thinking about decision making with computers, and the computer's relationship to the brain for too long now, and before I get dementia (I'm 35) I would like to put a stake in the ground and tell everyone where they can stick their thoughts about the future. 

I am simultaneously very hopeful for the future and horrified by the way that people talk about it. I think many so-called "Data Scientists" are full of shit when they talk, and some of them know it but would like to keep their jobs. I think that many investors are snowed by fancy language and toy demos that they extrapolate into a magical future. Users of digital products are woefully ignorant about how the products work and how they fit into a larger ecosystem. I'm amused, annoyed and would like to clear things up for everyone, including myself.

I am a self-employed programmer and financially secure, these are my credentials. I have no corporate master and I am not raising money to create the future of AI, so have a limited bias towards AI boosterism. I write programs close enough to the bleeding-edge that I can see the present as fast as almost anyone. Because I am simultaneously a contractor (\url{https://inoxoft.com/}), investor (\url{https://ventures.nextfab.com/about/}) and teacher (\url{https://bradflaugher.com/bootcamp.html}) I get the opportunity to see many projects, and I hope I can effectively comment on some common misconceptions and errors in thinking I see in many businesspeople, developers and investors.

So let's go on this journey together, I'll try and explain to you (with words, code and examples) how modern AI works, and when you should be scared (self-driving cars without the appropriate infrastructure) or when you should not be scared (please shut up about Skynet becoming self-aware). I'll also try do case studies in as many arenas that I think are interesting. If you have notes for me you can reach me at \href{mailto:brad@bradflaugher.com}{brad@bradflaugher.com}.

Please skim this book, please skip around and read some stories. I think the first three chapters are important for everyone to know. The rest of the stories can be chosen a la carte. Enjoy.

\begin{flushright}
	\textit{Brad Flaugher}
\end{flushright}

PS Thank you Angela Altamirano for the cover wonderful cover art. Thank you to my early supporters, William Dickson, Daniel Hoevel, Patrick Maloney, Jerrod Howlett and Jeff Zinser. A special thank you to Louis Cid and the Harvard Club of New York for giving me an early forum. Finally thank you to Dr. Péter Érdi for putting me under his wing many years ago and Dr. Elisa Esposito for her constant support. 

PPS This book uses the wonderful Free and Open Source Kaobook LaTeX project (\url{https://github.com/fmarotta/kaobook}) and  many Free and Open Source AI  models for text and image generation like Stable Diffusion (\url{https://huggingface.co/spaces/stabilityai/stable-diffusion}) and Mann-E (\url{https://huggingface.co/mann-e/mann-e_4_rev-0-1}) and some closed models like GPT-3, ChatGPT and Dall-E from OpenAI (\url{https://openai.com/}).
